European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
demo: reformat

    -   IMF loan to GDP ratio

    -   IMF participation rate

    -   IMF loan approval

    -   IMF conditions

@@

    -   GDP

    -   Growth

    -   Reserves

    -   OECD

@@

```{r setup}
need <- c('AER','car','kableExtra','modelsummary','parameters') # list packages needed
# have <- need %in% rownames(installed.packages()) # checks packages you have
# if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only = T))
```

@@

#t-tests
regtable$`Probit: IMF loan approval`$df.residual <- degrees_of_freedom(regtable$`Probit: IMF loan approval`)

glance_custom.tobit <- function(x, ...) {
  data.frame(
    'equality'=paste0('[','$p=',round(lht(x, test='F', 'us=eu')[2,4],3),'$]'),
    'vcov.type' = 'by: Country'
  )
}

glance_custom.fixest <- function(x, ...) {
  data.frame(
    'equality'=paste0('[','$p=',round(lht(x, test='F', 'us=eu')[2,4],3),'$]'),
    'vcov.type' = 'by: Country'
  )
}

coefmap <- c('us' = 'US Influence',
             'eu' = 'EU Influence',
             'imf' = 'IMF Influence',
             'lnrgdpnew' = 'GDP',
             'lnrgdpnewsq' = 'GDP$^2$',
             'rgdpchnew' = 'GDPpc',
             'rgdpchnewsquare' = "GDPpc$^2$",
             'growth1new' = 'GDPpc growth',
             'reserv1' = 'Reserves',
             'oecd1' = 'OECD',
              '(Intercept)' = '(Intercept)')
gof_map <- list(list("raw" = "equality", "clean" = "US=EU", "fmt" = NULL),
                list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
                list('raw' = 'vcov.type', 'clean' = 'Std.Errors', 'fmt' = NULL))
msummary(regtable, coef_map=coefmap, gof_map=gof_map, stars=T, escape=F, output = "kableExtra") |>
  kable_styling(latex_options="scale_down")
```

>>>>

    -   IMF loan to GDP ratio, IMF participation rate

    -   IMF loan approval, IMF conditions

@@

    -   GDP, Growth

    -   Reserves, OECD

@@

```{r setup}
need <- c('AER', 'car', 'kableExtra', 'modelsummary', 'parameters') # list packages needed
# have <- need %in% rownames(installed.packages()) # checks packages you have
# if(any(!have)) install.packages(need[!have]) # install missing packages
invisible(lapply(need, library, character.only = T))
```

@@

#t-tests
regtable$`Probit: IMF loan approval`$df.residual <- degrees_of_freedom(
  regtable$`Probit: IMF loan approval`
)

glance_custom.tobit <- function(x, ...) {
  data.frame(
    'equality' = paste0(
      '[',
      '$p=',
      round(lht(x, test = 'F', 'us=eu')[2, 4], 3),
      '$]'
    ),
    'vcov.type' = 'by: Country'
  )
}

glance_custom.fixest <- function(x, ...) {
  data.frame(
    'equality' = paste0(
      '[',
      '$p=',
      round(lht(x, test = 'F', 'us=eu')[2, 4], 3),
      '$]'
    ),
    'vcov.type' = 'by: Country'
  )
}

coefmap <- c(
  'us' = 'US Influence',
  'eu' = 'EU Influence',
  'imf' = 'IMF Influence',
  'lnrgdpnew' = 'GDP',
  'lnrgdpnewsq' = 'GDP$^2$',
  'rgdpchnew' = 'GDPpc',
  'rgdpchnewsquare' = "GDPpc$^2$",
  'growth1new' = 'GDPpc growth',
  'reserv1' = 'Reserves',
  'oecd1' = 'OECD',
  '(Intercept)' = '(Intercept)'
)
gof_map <- list(
  list("raw" = "equality", "clean" = "US=EU", "fmt" = NULL),
  list("raw" = "nobs", "clean" = "$N$", "fmt" = 0),
  list('raw' = 'vcov.type', 'clean' = 'Std.Errors', 'fmt' = NULL)
)
msummary(
  regtable,
  coef_map = coefmap,
  gof_map = gof_map,
  stars = T,
  escape = F,
  output = "kableExtra"
) |>
  kable_styling(latex_options = "scale_down")
```
